Boosted

### 2016-05-25 boost_tree.rmd
Aleysha commit

>>>>

Try discretising total amount invoiced for the job.

Try tuning with caret package including Business and all years

#decide how many clusters
x<- dist(all9c$inv.mlsto.log, method = 'euclidean')
fit<- hclust(x, method = 'ward.D2')
plot(fit)

# optimise number of clusters
clusts = c(4, 5,7,9)
for(j in seq_along(clusts)){

all9c$b.inv.log<- as.factor(cutree(fit, k= clusts[j]))

formula<- "b.rpdol ~ Discipline + pc.pro + b.timespan.cbrt + no.users + b.inv.log +
client.totinv.log + pc.majpos.log + Billing.Type + majority.pos + Business"

cv.Control <- trainControl(method = "cv",
                           number = 5,
                           seeds= seeds
                           , summaryFunction=twoClassSummary,
                           classProbs=TRUE
                           )
gbmGrid <- expand.grid(shrinkage = c(0.001),
                       n.trees = c(10000), interaction.depth = c(5),
                       n.minobsinnode = c(20))
set.seed(2)
gbmFit <- train(as.formula(formula), data= train2,
                 method = "gbm", trControl = cv.Control, verbose = FALSE,
                 bag.fraction = 0.5, tuneGrid = gbmGrid,
                metric = 'ROC',
                na.action = na.pass)

assign(paste("gbmFit",j,sep = ""), gbmFit, envir = .GlobalEnv)
}

AUCs = c(gbmFit4$results$ROC, gbmFit1$results$ROC, gbmFit2$results$ROC, gbmFit3$results$ROC)
plot = data.frame(no.clusts = clusts, AUC = AUCs)
ggplot(plot, aes(x = no.clusts %>% as.numeric, y = AUC)) + geom_line()

# therefore:
# shrinkage = 0.001
# no trees = 10000
# min terminal node size = 20
# max tree depth = 5

# AUC approx 0.748 for 5 clusters of invoiced amount for job = best
#

Tune boosted tree for 5 clusters of job invoice size

#decide how many clusters
x<- dist(all9c$inv.mlsto.log, method = 'euclidean')
fit<- hclust(x, method = 'ward.D2')
plot(fit)
rect.hclust(fit, k = 5)

#assign a cluster number to all rows in data frame
all9c$b.inv.log<- as.factor(cutree(fit, k=5))
head(all9c$b.inv.log)

key = all9c %>% group_by(b.inv.log) %>% summarise(min = min(inv.mlsto.log) %>% exp() %>% round(0), max = max(inv.mlsto.log) %>% exp() %>% round(0))

arrange(key, min)
key$min %>% round(-2)
breaks = c(100,600,2500,8000,60000, 1800000)
breaks = sort(breaks)
log(breaks)

#create clusters based on summary:
man.clust<- function(first.vec=all9c$timespan.cbrt, breaks.man=c(0,4.16,6.558,15),
                     labs = c("t0_70", "t70_280", "t280_")){
        final = cut(first.vec, breaks=breaks.man, include.lowest=TRUE, labels= labs)
        return(final)
}

#inv.mlsto.log

all9c$b.inv.log <- man.clust(first.vec=all9c$inv.mlsto.log, 
                            breaks.man= log(breaks),
                            labs = c("100-600","600-2.5k","2.5k-8k","8k-60k","60k-1.8m"
                            ))

formula<- "b.rpdol ~ Discipline + pc.pro + b.timespan.cbrt + no.users + b.inv.log +
client.totinv.log + pc.majpos.log + Billing.Type + majority.pos + Business"

cv.Control <- trainControl(method = "cv",
                           number = 5,
                           seeds= seeds
                           , summaryFunction=twoClassSummary,
                           classProbs=TRUE
                           )
gbmGrid <- expand.grid(shrinkage = c(0.001),
                       n.trees = c(10000), interaction.depth = c(3,4,5,6),
                       n.minobsinnode = c(20))
set.seed(2)
gbmFit <- train(as.formula(formula), data= train2,
                 method = "gbm", trControl = cv.Control, verbose = FALSE,
                 bag.fraction = 0.5, tuneGrid = gbmGrid,
                metric = 'ROC',
                na.action = na.pass)

plot(gbmFit)

# interaction depth = 5 is best

write.csv(all9c, 'C:/Users/n9232371/Documents/Consultbusiness/data/all9c.csv')
write.csv(all9c, 'C:/Users/n9232371/OneDrive/shared files/Bligh Tanner/masters/data/all9c.csv')
